\documentclass{resume}

\usepackage[left=0.75in,top=0.51in,right=0.75in,bottom=0.51in]{geometry}
\usepackage{hyperref,xcolor}
\usepackage[ocgcolorlinks]{ocgx2}

\hypersetup{allcolors=blue}

\name{Luke Jianu}
\address{{+1(425) 229-1106} \\ 
        {jianuluke@gmail.com} \\
        \href{https://github.com/lukejianu}{github/lukejianu} \\
        \href{https://www.linkedin.com/in/lukejianu/}{linkedin/lukejianu}}

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}
  \begin{rSection}{Education}

    \begin{rSubsection}{Northeastern University}{Sept. 2021 - May 2025}
      {\normalfont B.S. in Computer Science, 4.00/4.00 GPA, Dean's Merit Scholarship}{Boston, MA}
      \begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
          \emph{Relevant} & Software Development, Object-Oriented Design, Algorithms \& Data \\
          \emph{Coursework} & Computer Systems, Programming Languages, Database Design \\
      \end{tabular}

      \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        \emph{Teaching} & Software Development, \href{https://felleisen.org/matthias/}{Matthias Felleisen} (Fall 2024) \\
        \emph{Assistant} & Logic \& Computation, \href{https://dbp.io/}{Daniel Patterson} (Spring 2024) \\
      \end{tabular}

    \end{rSubsection}

  \end{rSection}
  \begin{rSection}{Experience}

    \begin{rSubsection}{Databricks}{May 2024 - Aug. 2024}{Incoming Software Engineer Intern}{Bellevue, WA}
    \end{rSubsection}

    \begin{rSubsection}{Belvedere Trading}{June 2023 - Aug. 2023}{Software Engineer Intern}{Chicago, IL}
      \item Built a low-latency, service-agnostic proxy in C++ to aggregate redundant TCP
        connections between datacenters, resulting in a \textbf{70\% reduction} in bandwidth usage for proxied services.
      \item Optimized performance through the use of asynchronous message passing, implemented with the visitor
        design pattern (std::visit), enabling the processing of \textbf{5.4Tb of data} daily.      
      \item Upgraded the C\# service discovery algorithm to match clients with services in the same datacenter.
    \end{rSubsection}

    \begin{rSubsection}{Amazon Robotics}{Jan. 2023 - June 2023}{Software Development Engineer Co-op}{North Reading, MA}
      \item Empowered AR teams to rapidly grow, monitor and manage their device fleets at scale by inventing and simplifying
        features in my team's 
        \href{https://www.allthingsdistributed.com/2021/07/amazon-robotics-on-aws.html}{Comprehensive Device Management} solution. 
      \item Architected an efficient, fault-tolerant workflow in AWS Lambda with Kotlin for modifying 
        robot location data, enabling teams to avoid \textbf{1000+ hours} of OS and software reinstalls yearly.
      \item Designed a device timeline feature in AWS CDK with TypeScript, providing insights for \textbf{30k+ devices}. 
      \item Refactored a large, imperative-style vanilla React codebase with functional-style 
        TypeScript \& React Query, resulting in a \textbf{95\% reduction} in API calls and \textbf{50\% faster} loading times.
    \end{rSubsection}

    \begin{rSubsection}{S3Global}{May 2022 - Aug. 2022}{Software Development Intern}{Redmond, WA}
    \item Designed C++ tooling for benchmarking, testing, and managing 
      \textbf{\href{https://emergentvisiontec.com/}{12 high-speed cameras}} used to capture 
        computer vision training data from the top youth football academies in Spain.
      \item Implemented a prototype video streaming system with shared frame buffers, leveraging C++ interop with the camera's SDK
        to display frames in a C\# WPF frontend.
    \end{rSubsection}

  \end{rSection}
 \begin{rSection}{Projects}

   \begin{rSubsection}{Rust Operating System}{Dec. 2023 - Present}{}{}
   \item Designing and developing a small OS in Rust, with a focus on systematic design, loosely
     following the blog post \href{https://os.phil-opp.com/}{\emph{Writing an OS in Rust} by Phillip Oppermann}.
    \end{rSubsection}

   \end{rSection}
  
  \begin{rSection}{Technical Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Programming Languages & Java, C++, Python, JavaScript, TypeScript, SQL \\
      Tools \& Technologies & Vim, Linux, Git, AWS, Docker, Node, React, Prisma, Flask, Splunk
    \end{tabular}
  \end{rSection}

\end{document}

