\documentclass{resume}

\usepackage[left=0.75in,top=0.51in,right=0.75in,bottom=0.51in]{geometry}
\usepackage{hyperref}

\name{Luke Jianu}
\address{{+1 (425) 229-1106} \\ 
        {jianuluke@gmail.com} \\
        \href{https://github.com/lukejianu}{github/lukejianu} \\
        \href{https://www.linkedin.com/in/lukejianu/}{linkedin/lukejianu}}

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}
    \vspace{-4pt}
  \begin{rSection}{Education}
    \begin{rSubsection}{Northeastern University}{Sept. 2021 - May 2025}
    {\normalfont B.S. in Computer Science, 4.00/4.00 GPA}{Boston, MA}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        \emph{Relevant} & Object-Oriented Design, Algorithms \& Data, Fundamentals of CS I \& II \\
        \emph{Coursework} & Database Design, Foundations of Data Science, Foundations of Cybersecurity \\
        & Logic \&  Computation, Discrete Mathematics, Mathematics of Data Models \\
    \end{tabular} 
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        
    \end{tabular} 
    \end{rSubsection}
  \end{rSection}
  
  \vspace{-14pt}
  
  \begin{rSection}{Experience}
    \begin{rSubsection}{Belvedere Trading}{Jun. 2023 - Aug. 2023}{Incoming Software Engineer Intern}{Chicago, IL}
        \item Enhancing Belvedere’s high-performance, low-latency proprietary technology.
    \end{rSubsection}
    \begin{rSubsection}{Amazon Robotics}{Jan. 2023 - Jun. 2023}{Software Development Engineer Co-op}{North Reading, MA}
        \item Empowered AR teams to rapidly grow, monitor and manage their device fleets at scale by inventing and simplifying features in my team's \href{https://www.allthingsdistributed.com/2021/07/amazon-robotics-on-aws.html}{Comprehensive Device Management} solution. 
        \item Designed a device timeline feature, providing troubleshooting insights for \textbf{30k+ devices}. This feature was vended as an AWS CDK construct, built with AWS Lambda, Dynamo, and IoT resources. 
    \item Architected a move device system in AWS Lambda with Kotlin, enabling teams to
        provision robotic workcells in test sites, saving \textbf{1000+ hours} of software installs yearly for IT at production sites.
        \item Refactored a large, imperative-style vanilla React codebase with functional-style TypeScript \& React Query. Further DX improvements included the addition of ESLint, Prettier, and developer docs. 
        \item Optimized UI speed and usability by \textbf{200\%} by caching customer selection from previous sessions, using React Router to remove page reloads, and adding URL params to replicate state when sharing links.
    \end{rSubsection}
    \begin{rSubsection}{S3Global}{May 2022 - Aug. 2022}{Software Development Intern}{Redmond, WA}
        \item Built a .NET application to interface with \href{https://emergentvisiontec.com/}{high-speed cameras}, implemented using WPF in C\# and \\ C++ interop with the camera's SDK to dump frames into shared buffers for video streaming.
    \end{rSubsection}
    \begin{rSubsection}{Seattle Sport Sciences}{May 2021 - Aug. 2021}{Intern}{Redmond, WA}
        \item Conducted data trials for cloud-based AI/ML analysis of \textbf{30+ soccer matches}, while also performing maintenance and troubleshooting for camera hardware, network connections, and deployment tools.
    \end{rSubsection}
  \end{rSection}
  
  \vspace{-12pt}
  \begin{rSection}{Projects}
    \begin{rSubsection}{NUCarpool}{Sept. 2022 - Present}{Software Developer at Sandbox}{Boston, MA}
        \item Developing a web app using the T3 stack for Northeastern students to find co-op carpool groups.
    \end{rSubsection}
    \begin{rSubsection}{Trading Bot}{Jul. 2022}{Participant at Jane Street's Electronic Trading Challenge}{Seattle, WA}
        \item Traded securities using bond penny-pinching and ADR and ETF arbitrage strategies implemented in Python, ultimately placing \textbf{10\textsuperscript{th} out of 32 teams}. 
    \end{rSubsection}

   \end{rSection}
   \vspace{-12pt}
   
  \begin{rSection}{Technical Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Computer Languages & Python, Java, JavaScript, TypeScript, SQL \\
      Tools \& Technologies & Vim, Git, AWS, Docker, React, Prisma, Flask
    \end{tabular}
  \end{rSection}
\end{document}
